
% \part{Erster Teil} % Teile nur bei sehr langen Arbeiten

\chapter{Introduction}
\label{chapter:introduction}
\section{Description of KIELER}
\label{sec:intro/Kieler}
\begin{itemize}
 \item layouter, structure based editing
 \item synchcharts
 \item simulater
 \item execution manager
\end{itemize}
\section{Description of the KIEM}
\label{sec:intro/Kiem}
Execution Manager is used in KIELER as a framework to plug-in DataComponents for various tasks. Examples are:
\begin{itemize}
 \item Simulation Engines
 \item Model Visualizers
 \item Environment Visualizers
 \item Validators
 \item User Input Facilities
 \item Trace Recording Facilities 
\end{itemize}

These DataComponents can be executed using a graphical user interface (GUI). 
The scheduling order can also be defined by this GUI as well as other settings like a step/tick duration and properties of DataComponents.
For information about \ac{KIEM} see - \url{http://rtsys.informatik.uni-kiel.de/trac/kieler/wiki/Projects/KIEM}
\section{Outline of this Document}
\label{sec:intro/Outline}
The first part of this document is about the implemention of the Configuration plugin for the \ac{KIEM}.
The second part is about the implementation of an Automated Execution plugin for the \ac{KIEM}. Both
parts will have the same structure described below.
Each part starts with a detailed outline of the problems that are to be solved by this thesis.
The next section will be about the technologies used to solve the problem.
After that there will be a section about the concepts of how to solve the problem and some
design decisions that were made at a very early stage in the development.
Sections 5 and 6 are about the actual implementation with section 5 outlining the changes
that were made to the \ac{KIEM} plug-in itself and section 6 describing the newly created
\ac{KIEMConfig} plug-in.
The final section of each part will summarize the results of the thesis and outline
a few projects that could be based on it.







%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End: 

